Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
Done merging. Getting an error when converting to pdf
Fixed merger issues.

In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description and evaluation of functions in mathematics (Haskell). Lambda calculus became the foundation for functional programming (``Haskell''). However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there became the need for a standard functional language to aid the spread of functional programming (Hudak 1). A meeting was held in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need (Hudak 1). The meeting resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: a consolidation of existing functional programming languages into an open standard, common language to be used for functional programming research (Hudak 3). They named this language Haskell after Haskell Curry, a logician whose work greatly contributed to functional programming,
and chose the lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects of computing.

>>>>

In the early 1930s, Alonzo Church formulated a mathematical abstraction known as lambda calculus, which involves the description 
and evaluation of functions in mathematics. Lambda calculus became the foundation for functional programming~\cite{haskell-wiki}. 
However, as numerous functional languages began to develop, all of which were similar in expressiveness and semantics, there 
became the need for a standard functional language to aid the spread of functional programming. A meeting was held 
in 1987 at a Functional Programming Languages and Computer Architecture conference to address this need~\cite{hudak-hist}. The meeting 
resulted in the formation of a committee to design a standard functional language. In 1990, the committee produced their result: 
a consolidation of existing functional programming languages into an open standard, common language to be used for 
functional programming research: Haskell~\cite{hudak-con}.

Haskell is named after Haskell Curry, a logician whose work greatly contributed to functional programming. It has a 
lambda as its logo to symbolize lambda calculus as its foundation. Today, Haskell is widely used in many different aspects 
of computing. From AT\&T's automated processing of abuse complaints in its network security division to the National 
Radio Astronomy Observatory’s implementation of core science algorithms, Haskell can be found in many aspects of 
modern industry~\cite{haskell-wiki}.
